\section{Authors' Biographies}\label{sec:Biographies}
    E. Michael Bearss is a senior software engineer at Trideum Corporation working
    at the Redstone Test Center in Huntsville, AL\@.
    He is a CMSP and has multiple years of experience in LVC simulation.
    He is currently a Ph.D.\ student in Computer Science at the
    University of Alabama in Huntsville.
    He previously received an M.S.\ degree in Computer Science from the
    Georgia Institute of Technology.

    Walter Alan Cantrell is an Instructor in the College of Computing and Technology
    at Lipscomb University and a Director of Information Technology Service Management
    in the Core Infrastructure department at Vanderbilt University Medical Center.
    He received a Ph.D.\ in Modeling and Simulation at the University of Alabama
    in Huntsville in 2021.

    Christian W. Hall is a visiting research intern at the Applied Systems Laboratory
    under Georgia Tech Research Institute in Huntsville, AL\@.
    He is currently a B.S.\ student in Computer Science and Mathematics at the University
    of Alabama in Huntsville, where he also serves as a tutor and student grader for the
    Computer Science department.

    Joy E. Pinckard \ldots

    Mikel D. Petty is Senior Scientist for Modeling and Simulation and an
    Associate Professor of Computer Science at the University of Alabama in Huntsville.
    He received a Ph.D.\ in Computer Science from the University of Central Florida in 1997.
    Dr. Petty has worked in modeling and simulation R\&D since 1990 in areas that include
    verification and validation methods, simulation interoperability and composability,
    and cybersecurity modeling.
